---
title: "Practical 11B - Examples"
author: "sakith thewmika"
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Histogram Representation in R-Studio

A histogram is a graphical representation that organizes a group of data points into specified
ranges (bins). It helps to visualize the distribution of a dataset. Below is a guide to creating
histograms in RStudio with examples and corresponding code.

Example 1: Basic Histogram
```{r}
# Sample Data
weights <- c(10, 20, 30, 40, 50, 60, 70, 80, 90, 100)
# Creating Histogram
hist(weights, main = "Weight Distribution", xlab = "Weight (Kg)", col = "blue")

```

Example 2: Customized Histogram
```{r}
# Sample Data
weights <- c(5, 12, 19, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80)
# Creating Histogram with Custom Bins
hist(weights, breaks = 7, main = "Customized Histogram", xlab = "Weight (Kg)", col =
"green", border = "black")
```

Example 3: Histogram with Axis and Color Customization
```{r}
# Sample Data
weights <- c(10, 20, 30, 40, 50, 60, 70, 80, 90, 100)
# Creating Histogram
hist(weights, main = "Weight Distribution", xlab = "Weight (Kg)", col = "blue")
```
```{r}
# Sample Data
weights <- c(5, 12, 19, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80)
# Creating Histogram with Custom Bins
hist(weights, breaks = 7, main = "Customized Histogram", xlab = "Weight (Kg)", 
     col ="green", border = "black")
```

Example 4: Histogram with Specific Bar Width
```{r}
# Sample Data
weights <- c(8, 15, 22, 29, 35, 41, 47, 53, 59, 65, 71, 77, 83, 89, 95)
# Creating Histogram with Axis Customization
hist(weights, breaks = seq(0, 100, by = 10),
     main = "Weight Distribution",
     xlab = "Weight (Kg)",
     col = "red",
     xlim = c(0, 100),
     ylim = c(0, 5),
     border = "black")
```
```{r}
# Sample Data
weights <- c(9, 14, 21, 26, 32, 37, 42, 48, 53, 58, 63, 69, 74, 79, 85)
# Creating Histogram with Defined Bar Width
hist(weights, breaks = seq(0, 90, by = 10),
main = "Histogram with Defined Bar Width",
xlab = "Weight (Kg)",
col = "purple",
border = "black")
```
